Considering scale in multilayer animal social networks

### 2020-06-25 paper/manuscript.Rmd
fix order of figures
oops
fix order

# Results
Individuals in multilayer networks became more connected as the spatial distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in foraging and open layers, and lower
strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength decreased. 
GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
confirm the use of 50 m buffer that has long been used for studies in the field
[@Lingle_2003; @Clutton_1982]

Increasing land cover resolution resulted in decreased availability of foraging
habitat and corresponding low connectivity of individuals at higher land cover
resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
contrast, edge overlap was relatively consistent across land cover resolutions
in forest and open layers (Figure \@ref(fig:lcres) D).  Graph strength was more
variable within foraging habitat layers across land cover resolutions than open
and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
relocations in forest (42.1% at 30 m - 48.2% at 1000 m) and open (43.3% at 30 m
- 50.3% at 1000 m) habitats increased with increasing spatial resolution, while
decreasing in foraging habitat (14.5% at 30 m - <2% at 1000 m).  Overall, these
results indicate the importance of matching land cover resolution to scale of
selection as well as ensuring the land cover product used has a resolution fine
enough to detect landscape features and habitats relevant to study species, such
as important patchy and rare habitats.

The temporal multilayer network indicated within-year time windows where social 
network metrics increased. Edge overlap was higher in time windows 1, 6-11 and 
15-20 (between `r timedefs[timecut == 1, paste(mindate, maxdate, sep = ' and ')]`,
`r timedefs[timecut %in% 6:11, paste(min(mindate), max(maxdate), sep = ' and ')]`
and `r timedefs[timecut %in% 15:20, paste(min(mindate), max(maxdate), sep = ' and ')]`)
than in time windows 2-5 and 12-15 (between 
`r timedefs[timecut %in% 2:5, paste(min(mindate), max(maxdate), sep = ' and ')]`
and `r timedefs[timecut %in% 12:15, paste(min(mindate), max(maxdate), sep = ' and ')]`)
(Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between 
approximately October and June, also had higher graph strength 
compared to time windows of lower edge overlap, between approximately June 
and October (Figure \@ref(fig:temp) C). Graph strength peaked across the time 
series between  
`r timedefs[timecut %in% 9:10, paste(min(mindate), max(maxdate), sep = ' and ')]`. 
These results suggest that ordinal multilayer networks can effectively 
capture discrete time windows of aggregation and dissaggregation related 
to resource availability, and highlight the importance of carefully 
selecting the temporal scale of analysis.

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased.
Graph strength across individuals in all three habitat layers was highly
variable at low number of observations and variance decreased after ~100 observations
(Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations, and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C). Given the observed trend of these multilayer metrics
decreasing in variance after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing social dynamics across
contexts.

>>>>

# Results
Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in foraging and open layers, and lower
strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength decreased. 
GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
confirm the use of 50 m buffer that has long been used for studies in the field
[@Lingle_2003; @Clutton_1982]

Increasing land cover resolution resulted in decreased availability of foraging
habitat and corresponding low connectivity of individuals at higher land cover
resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
contrast, edge overlap was relatively consistent across land cover resolutions
in forest and open layers (Figure \@ref(fig:lcres) D).  Graph strength was more
variable within foraging habitat layers across land cover resolutions than open
and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
relocations in forest (42.1% at 30 m - 48.2% at 1000 m) and open (43.3% at 30 m
- 50.3% at 1000 m) habitats increased with increasing spatial resolution, while
decreasing in foraging habitat (14.5% at 30 m - <2% at 1000 m).  <!-- TODO: 
break up -->Overall, these
results indicate the importance of matching land cover resolution to scale of
habitat selection as well as ensuring the land cover product used has a resolution fine
enough to detect landscape features and habitats relevant to study species, such
as important patchy and rare habitats.

The temporal multilayer network indicated within-year time windows where social 
network metrics increased. Edge overlap was higher in time windows 1, 6-11 and 
15-20 (between `r timedefs[timecut == 1, paste(mindate, maxdate, sep = ' and ')]`,
`r timedefs[timecut %in% 6:11, paste(min(mindate), max(maxdate), sep = ' and ')]`
and `r timedefs[timecut %in% 15:20, paste(min(mindate), max(maxdate), sep = ' and ')]`)
than in time windows 2-5 and 12-15 (between 
`r timedefs[timecut %in% 2:5, paste(min(mindate), max(maxdate), sep = ' and ')]`
and `r timedefs[timecut %in% 12:15, paste(min(mindate), max(maxdate), sep = ' and ')]`)
(Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between 
approximately October and June, also had higher graph strength 
compared to time windows of lower edge overlap, between approximately June 
and October (Figure \@ref(fig:temp) C). Graph strength peaked across the time 
series between  
`r timedefs[timecut %in% 9:10, paste(min(mindate), max(maxdate), sep = ' and ')]`. 
These results suggest that ordinal multilayer networks can effectively 
capture discrete time windows of aggregation and dissaggregation related 
to resource availability, and highlight the importance of carefully 
selecting the temporal scale of analysis. <!-- TODO see comment-->

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased.
Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations, and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C). Graph strength across individuals in all three habitat layers was highly
variable at low number of observations and variance decreased after ~100 observations
(Figure \@ref(fig:nobs) A). Given the observed trend of these multilayer metrics
decreasing in variance after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing social dynamics across
contexts.
